Reproducibility of SNP calling in multiple sequencing runs from single tumors

### 2014-10-28 PAPER/paper_d1.tex
fixed figures

\begin{figure}
\includegraphics[scale=1.0]{unfiltered_total_muts_v_percent_overlap.png}
\caption{\textbf{Percent of WGS/WGA overlap versus (log) number of putative SNPs per sample.} Plot of the percentage of the WGA samples that overlaped with the corresponding WGS samples (as a measure of sample quality) against the total number of putative SNPs in the WGS sample}
\end{figure}

@@

% this is not the final path name, because this is not the final figure
\begin{figure}
\includegraphics[scale=1.0]{/Users/dakota/Desktop/other_computer/LOH_all.png}
\caption{\textbf{Length of overlap of LOH segments.} As the length of the overlap between WGS and WGA increases (x-axis), the number of mutaitons filtered out by LOH increases. This is the opposite of the pattern observed in VAQ mutaitons (figure 6).}
\end{figure}

% this is not the final path name, because this is not the final figure
\begin{figure}
\includegraphics[scale=1.0]{/Users/dakota/Desktop/other_computer/VAQ_all.png}
\caption{ \textbf{Length of overlap of VAQ segments.} As the length of the overlap between WGS and WGA increases (x-axis), the number of mutaitons filtered out by VAQ decreases. This is the opposite of the pattern observed in LOH mutaitons (figure 5).}
\end{figure}

>>>>

\begin{figure}
\includegraphics[scale=1.0]{unfiltered_total_muts_v_percent_overlap.png}
\caption{\textbf{Percent of WGS/WGA overlap versus (log) number of putative SNPs per sample.} Plot of the percentage of the WGA samples that overlaped with the corresponding WGS samples (as a measure of sample quality) against the total number of putative SNPs in the WGS sample.}
\end{figure}

@@

% this is not the final path name, because this is not the final figure
\begin{figure}
\includegraphics[scale=1.0]{./LOH_VAQ/LOH_all.png}
\caption{\textbf{Length of overlap of LOH segments.} As the length of the overlap between WGS and WGA increases (x-axis), the number of mutaitons filtered out by LOH increases. This is the opposite of the pattern observed in VAQ mutaitons (figure 6).}
\end{figure}

% this is not the final path name, because this is not the final figure
\begin{figure}
\includegraphics[scale=1.0]{./LOH_VAQ/VAQ_all.png}
\caption{ \textbf{Length of overlap of VAQ segments.} As the length of the overlap between WGS and WGA increases (x-axis), the number of mutaitons filtered out by VAQ decreases. This is the opposite of the pattern observed in LOH mutaitons (figure 5).}
\end{figure}
